---
author: 'Naomi A. Boss'
date: 'December 2020'
institution: 'Reed College'
division: 'Mathematics and Natural Sciences'
advisor: 'Andrew P. Bray'
# If you have more two advisors, un-silence line 7
#altadvisor: 'Your Other Advisor'
department: 'Mathematics'
degree: 'Bachelor of Arts'
title: 'My Final College Paper'
knit: "bookdown::render_book"
site: bookdown::bookdown_site
output: 
  thesisdown::thesis_pdf: default
#  thesisdown::thesis_gitbook: default
#  thesisdown::thesis_word: default
#  thesisdown::thesis_epub: default
# If you are creating a PDF you'll need to write your preliminary content (e.g., abstract, acknowledgements) here or
# use code similar to line 22-23 for the .RMD files. If you are NOT producing a PDF, you can delete or silence lines 21-32 in this YAML header.
abstract: |
  `r if(knitr:::is_latex_output()) paste(readLines("00-abstract.Rmd"), collapse = '\n  ')`
# If you'd rather include the preliminary content in files instead of inline
# like below, use a command like that for the abstract above.  Note that a tab is 
# needed on the line after the `|`.
acknowledgements: |
  I want to thank a few people.
dedication: |
  You can have a dedication here if you wish. 
preface: |
  This is an example of a thesis setup to use the reed thesis document class
  (for LaTeX) and the R bookdown package, in general.
# Specify the location of the bibliography below
bibliography: bib/thesis.bib
# Download your specific csl file and refer to it in the line below.
csl: csl/apa.csl
lot: true
lof: true
# If you prefer blank lines between paragraphs, un-silence lines  40-41 (this requires package tikz)
#header-includes:
#- \usepackage{tikz}
---

# If you have more two advisors, un-silence line 7

Placeholder



<!--chapter:end:index.Rmd-->


# Literature Review {#lit-review}

* Probability Theory (establishing definitions)
     - Random Variables & Distributions
     - LLN & CLT

* Statistical Inference
     - frequentist v Bayesian
     - sampling distribution

* Survey Methodology
     - Sampling Procedures
          - Methods (section likely mixed rather than divided like so)
               - Simple random sampling
               - Stratified random sampling
               - Systematic sampling
               - Cluster 
               - Stratified sampling
          - Advantages/Disadvantages
     - Data Collection
          - Designing survey (sample unit, sample size, hypothesis/motivation role)
          - Survey method (brief list e.g. interview, questionnaire)
     - Data Analysis
          - Hypothesis testing
          - Inference
     
* Non-Probability Sampling
     - Sampling Procedures
          - Methods
               - Convenience sampling
               - Consecutive sampling
               - Judgmental Sampling
          *Advantages/Disadvantages
     - Data Collection
          - Designing Survey (sample unit, sample size, hypothesis/motivation role)
          - Survey method (brief list e.g. interview, questionnaire)
     - Data Analysis
          - Hypothesis testing
          - Inference
          
* Election Polling
     - Purpose
     - Design
          - Population
               - Sample selection
          - Methods
          - Sample size
          - Question design
               - Wording impacting response
     - Data collection
          - Implementation
          - Errors
               - Sampling Error
               - Non-Sampling Error
                    - Questionaire design
                    - Interviewer effects
                    - Responder effects
     - Data analysis
     


     


<!--chapter:end:01-chap1.Rmd-->

# tbd {#math-sci}

<!-- Required to number equations in HTML files -->
<script type="text/x-mathjax-config">
MathJax.Hub.Config({
  TeX: { equationNumbers: { autoNumber: "AMS" } }
});
</script>

<!--chapter:end:02-chap2.Rmd-->


# Tables, Graphics, References, and Labels {#ref-labels}

Placeholder


## Tables
## Figures
## Footnotes and Endnotes
## Bibliographies
## Anything else?

<!--chapter:end:03-chap3.Rmd-->

# Conclusion {-}

If we don't want Conclusion to have a chapter number next to it, we can add the `{-}` attribute.

**More info**

And here's some other random info: the first paragraph after a chapter title or section head _shouldn't be_ indented, because indents are to tell the reader that you're starting a new paragraph. Since that's obvious after a chapter or section title, proper typesetting doesn't add an indent there.


<!--chapter:end:04-conclusion.Rmd-->

`r if(knitr:::is_latex_output()) '\\appendix'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'` 

<!--
If you feel it necessary to include an appendix, it goes here.
-->


# The First Appendix

This first appendix includes all of the R chunks of code that were hidden throughout the document (using the `include = FALSE` chunk tag) to help with readibility and/or setup.

**In the main Rmd file**

```{r ref.label='include_packages', results='hide', echo = TRUE}
```

**In Chapter \@ref(ref-labels):**

```{r ref.label='include_packages_2', results='hide', echo = TRUE}
```

# The Second Appendix, for Fun

<!--chapter:end:05-appendix.Rmd-->


# References {-}

Placeholder



<!--chapter:end:99-references.Rmd-->

